\documentclass{resume}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\name{Lionel Verano IV}
\address{341-215-8440 \\ \href{mailto:lionel.verano.iv@berkeley.edu}{lionel.verano.iv@berkeley.edu} \\ \href{https://linkedin.com/in/lionelv2003}{linkedin.com/in/lionelv2003} \\ \href{https://lionelvlv.github.io/lionelvlv/}{lionelvlv.github.io/lionelvlv/}}

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\textbf{University of California, Berkeley} 
B.A. Computer Science\\
CS Scholar, Fiat Lux Scholar, Honor Student\\
Relevant Coursework: Computer Security, Computer Graphics, Internet Architecture, Artificial Intelligence, Data Engineering, Principles \& Techniques of Data Science, Fullstack Web Development
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Work and Leadership Experience}

\textbf{Computer Science Undergraduate Association — Root Staff} \hfill UC Berkeley, 2026–Present
\begin{itemize}
  \item Streamlined onboarding by rewriting technical documentation and setup guides, reducing new‑member setup time by 40\% and cutting recurring support questions.
  \item Resolved student environment issues and SSH key conflicts across 50+ support interactions, improving system access reliability and lowering repeat incidents.
  \item Automated internal workflows with lightweight Python and Bash scripts, eliminating 3--5 hours of manual officer work per month and standardizing routine tasks.
\end{itemize}

\textbf{Comprehensive Seating Chart for NAVCAL Facilitators — Freelance Developer} \hfill 2026–Present
\begin{itemize}
  \item Built a comprehensive seating-chart web app for NAVCAL facilitators featuring drag-and-drop seat assignment, automated cold-calling lists, advanced attendee filtering, and CSV/printable exports.
  \item Improved facilitator productivity by 400\% by drastically reducing setup time and streamlining outreach and check-in workflows.
  \item Integrated real-time syncing with Google Sheets and calendar systems to keep rosters and assignments current.
\end{itemize}

\textbf{RAMAR Foods International Accounts Receivable Portal — Freelance Developer} \hfill 2026–Present
\begin{itemize}
  \item Developed a secure accounts-receivable portal consolidating client resources, invoice tracking, messaging, and contact forms; secured file storage via Dropbox integration.
  \item Clients reported a ~40\% reduction in administrative coordination time and a ~30\% increase in timely client responses after centralizing resources on the portal.
  \item Implemented authentication, role-based access control, responsive UI, and HTTPS to ensure secure, convenient access for clients and staff.
\end{itemize}

\textbf{NAVCAL — Student Success Coordinator and Database Architect} \hfill UC Berkeley, 2024–Present
\begin{itemize}
  \item Automated scholarship-reminder workflows by building Google Apps Script systems that send targeted emails to students, reducing manual outreach and increasing response rates.
  \item Built a 100+-entry scholarship database with built-in verification logic, enabling accurate tracking and streamlined advising workflows.
  \item Facilitated academic workshops and directed support for course planning and financial aid for first-generation and non-traditional students.
\end{itemize}

\textbf{Social Sciences Research Pathways — Research Assistant} \hfill UC Berkeley, 2025–Present
\begin{itemize}
  \item Analyzing 10,000+ California election records in R, building data-processing pipelines to aggregate, filter, and model precinct-level voting patterns.
  \item Applying machine-learning methods to evaluate potential impacts of the California Voting Rights Act across multiple jurisdictions.
\end{itemize}

\textbf{CalAnime Newsletter — Co-Founder} \hfill 2022–2025
\begin{itemize}
  \item Founded and led collegiate anime publication reaching hundreds of readers across 13 colleges and universities.
  \item Recruited and trained team of 30 staff members; published 12 issues in first volume with consistent content quality.
  \item Established editorial processes, content strategy, and community engagement infrastructure across multiple platforms.
\end{itemize}

\textbf{Game Development at Berkeley — Lead Game Developer} \hfill Spring 2025 \\
\textit{UC Berkeley}
\begin{itemize}
  \item Directed a 4-person development team to build \textit{Fishing in the Clouds} in Unity, delivering a fully playable vertical slice within one semester and increasing team production velocity by 35\%.
  \item Implemented core gameplay systems including cloud‑platform traversal, fishing mechanics, and dynamic item spawning, improving playtest engagement time by over 40\%.
  \item Optimized performance and scene organization through prefab architecture and event-driven scripting, reducing frame drops by 25\% on mid-range hardware.
\end{itemize}


\textbf{Cal Animage Alpha — Technology Lead Web Developer} \hfill UC Berkeley, 2024–2025
\begin{itemize}
  \item Led 4-engineer team to build a Svelte event platform for 1,000+ attendees, delivering real-time schedules and announcements.
  \item Integrated secure Stripe payments to streamline registration and merchandise transactions.
\end{itemize}

\textbf{Cal Animage Alpha — Publicity Head} \hfill UC Berkeley, 2022–2023
\begin{itemize}
  \item Directed all social media channels with outreach of 1,000+ followers; increased engagement by 50\% in Spring 2023.
  \item Edited and produced video content resulting in 18.1\% increased views and 25.2\% increased watch time.
\end{itemize}

\textbf{ScholarMentors — Mentor} \hfill UC Berkeley, 2024–2025
\begin{itemize}
  \item Led a cohort with office hours, PIQ support, and financial aid guidance.
  \item Out of 4 mentees, 3 made it into their desired schools.
\end{itemize}

\textbf{Geopogo — Software Engineer Intern} \hfill UC Berkeley, 2024
\begin{itemize}
  \item Expanded build mode in Unreal Engine 5, implementing new assets and features resulting in a 73\% increase of new building placements.
  \item Developed and integrated new camera settings, expanding functionality by 75\%.
  \item Collaborated with designers to debug new features, reducing post-deployment issues.
\end{itemize}

\textbf{Data 8: The Foundations of Data Science — Academic Intern} \hfill UC Berkeley, 2023
\begin{itemize}
  \item Tutored over 30 peers in core course concepts during weekly lab sessions.
  \item Conducted a targeted review session leading to scores 10\% above class average.
\end{itemize}

\textbf{Game Development at Berkeley — Developer, Pigmental (Video Game)} \hfill UC Berkeley, 2022
\begin{itemize}
  \item Spearheaded the creation of essential UI elements such as health bars and damage indicators resulting in a 25\% increase in user satisfaction in playtesting.
  \item Contributed key features and design in the development of 'Pigmental', a roguelike video game, using Unity and C\#, progressing the game from concept to playable prototype.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\textbf{Network Protocol Simulator with Routing and Congestion Control} \hfill CS 168, 2026
\begin{itemize}
  \item Built discrete-event network simulator in Python implementing distance-vector and link-state routing protocols, analyzing convergence behavior and handling link failures.
  \item Implemented TCP congestion control algorithms (Reno, Tahoe, CUBIC) with slow-start, congestion avoidance, and fast recovery; benchmarked throughput and fairness.
  \item Simulated network topologies with varying bandwidth, latency, and packet loss; measured performance metrics including queue utilization and end-to-end delay.
\end{itemize}

\textbf{Interactive 3D Gaussian Splat Painting System — Final Project} \hfill CS 184, 2025
\begin{itemize}
  \item Built interactive 3D Gaussian splat painting system by extending Nerfstudio's Viser renderer, implementing real-time color editing tools for large point-cloud scenes with millions of Gaussians.
  \item Developed polyline-based brush-stroke selection algorithm by projecting 3D Gaussian centers into screen space and computing point-to-stroke distances.
  \item Implemented image-based color transfer using Pillow and NumPy, mapping 2D pixel values onto 3D splats through normalized coordinate projection.
\end{itemize}

\textbf{Real-Time Cloth Simulation with Spring-Mass Systems} \hfill CS 184, 2025
\begin{itemize}
  \item Implemented physically-based cloth simulation using spring-mass systems with structural, shearing, and bending constraints; applied Verlet integration for stable numerical solving.
  \item Developed collision detection and response algorithms for self-collisions and object interactions, using spatial hashing to optimize performance for meshes with 10,000+ vertices.
  \item Integrated GLSL shaders for realistic cloth rendering including Blinn-Phong, texture mapping, and environment-mapped reflections.
\end{itemize}

\textbf{Physically-Based Path Tracer with Global Illumination} \hfill CS 184, 2025
\begin{itemize}
  \item Built Monte Carlo path tracer implementing ray-primitive intersection tests, BVH acceleration structures, and direct/indirect illumination with importance sampling.
  \item Implemented BSDF materials including diffuse, mirror, glass, and microfacet models using Fresnel reflectance and multiple importance sampling.
  \item Optimized rendering performance through BVH tree construction using surface area heuristic, reducing render times from hours to minutes for scenes with 100K+ triangles.
\end{itemize}

\textbf{3D Mesh Editor with Geometric Modeling Operations} \hfill CS 184, 2025
\begin{itemize}
  \item Implemented half-edge data structure for efficient mesh representation and traversal; developed geometric operations including edge flips, edge splits, and loop subdivision for mesh refinement.
  \item Built Bezier curve and surface evaluation using de Casteljau's algorithm; implemented adaptive tessellation for efficient rendering of smooth curved surfaces.
  \item Created mesh upsampling algorithms increasing polygon count while preserving surface features; applied area-weighted vertex normals for smooth shading across triangle meshes.
\end{itemize}

\textbf{Triangle Rasterization Pipeline with Antialiasing} \hfill CS 184, 2025
\begin{itemize}
  \item Built complete 2D rasterization pipeline implementing point-in-triangle tests, supersampling antialiasing, and texture mapping with bilinear and trilinear interpolation.
  \item Developed transforms pipeline supporting translation, rotation, and scaling operations; implemented hierarchical modeling for animated scenes with inverse kinematics.
  \item Optimized pixel sampling with mipmap texture filtering, reducing aliasing artifacts by up to 16x through multi-level sampling strategies.
\end{itemize}

\textbf{Multi-Agent Pacman AI with Search and Learning Algorithms} \hfill CS 188, 2025
\begin{itemize}
  \item Implemented AI agents using A* search with custom heuristics, minimax with alpha-beta pruning, and expectimax for adversarial gameplay.
  \item Developed Q-learning and approximate Q-learning agents with feature-based representations, achieving 80\%+ win rates by learning optimal policies through temporal difference updates.
  \item Built probabilistic inference system using Bayes nets and particle filtering for ghost tracking in partially observable environments.
\end{itemize}

\textbf{Neural Network Architectures for Classification and Language Tasks} \hfill CS 188, 2025
\begin{itemize}
  \item Implemented neural networks from scratch in PyTorch including perceptrons, MLPs, CNNs, RNNs, and attention mechanisms to solve regression, MNIST digit classification, and language identification tasks.
  \item Built complete training pipelines with mini-batch gradient descent, cross-entropy loss, and backpropagation; achieved 97\%+ accuracy on MNIST and 81\%+ on language ID benchmarks.
  \item Optimized model performance through systematic hyperparameter tuning of learning rates, hidden layer sizes, and network depth.
\end{itemize}

\textbf{Cryptographically Secure File Sharing System in Go} \hfill CS 161, 2025
\begin{itemize}
  \item Built secure file-sharing system in Go with end-to-end encryption, user authentication via digital signatures, hierarchical access control with delegation and revocation, resilient to malicious servers.
  \item Implemented hybrid cryptography combining AES-256 symmetric encryption for file data with RSA public-key encryption for key exchange; used HMAC for integrity verification and tamper detection.
  \item Designed secure sharing protocol enabling owners to grant and revoke access efficiently through capability-based security model; developed comprehensive integration tests validating security properties against adversarial attacks.
\end{itemize}

\textbf{Custom Spam/Ham Email Classifier with Advanced Feature Engineering} \hfill DATA C100, 2024
\begin{itemize}
  \item Engineered 15+ custom text features including TF-IDF transformations, character n-grams, and punctuation ratios to capture spam indicators in 8,000+ email datasets.
  \item Implemented and compared Logistic Regression, Decision Trees, and Random Forests using scikit-learn, achieving 96\%+ test accuracy through systematic hyperparameter tuning and k-fold cross-validation.
\end{itemize}

\textbf{Cook County Housing Price Prediction System} \hfill DATA C100, 2024
\begin{itemize}
  \item Built end-to-end ML pipeline predicting home sale prices across 500,000+ records, incorporating 61 features including property characteristics, location data, and temporal variables.
  \item Performed comprehensive feature engineering creating polynomial terms, interaction features, and categorical encodings; applied Ridge and Lasso regularization to handle multicollinearity.
  \item Achieved top-quartile prediction accuracy on held-out test set through systematic model tuning and outlier handling.
\end{itemize}

\textbf{Semi-Structured Data Analysis with MongoDB} \hfill DATA C101, 2024
\begin{itemize}
  \item Designed complex MongoDB aggregation pipelines using PyMongo to query and transform nested JSON documents from Yelp's academic dataset with variable schemas.
  \item Built document-oriented data models leveraging embedded arrays and references, comparing performance tradeoffs between MongoDB's flexible schema and traditional relational databases.
  \item Performed update operations including upserts and bulk modifications with text indexing across 100,000+ documents.
\end{itemize}

\textbf{UC Berkeley Building Sensor Data Transformation Pipeline} \hfill DATA C101, 2024
\begin{itemize}
  \item Engineered ETL pipeline processing 1+ million sensor readings from UC Berkeley buildings, cleaning malformed timestamps, handling missing data, and normalizing measurement units.
  \item Designed normalized relational schema with proper foreign key constraints and indexing strategies, transforming denormalized CSV data into efficient PostgreSQL database structure optimized for billions of rows.
  \item Implemented complex SQL aggregations including window functions and CTEs to compute rolling averages and detect anomalies.
\end{itemize}

\textbf{Database Query Performance Optimization on Baseball Statistics} \hfill DATA C101, 2024
\begin{itemize}
  \item Analyzed query execution plans using EXPLAIN ANALYZE on Lahman's Baseball Database (1871-2020), identifying performance bottlenecks and optimizing slow queries.
  \item Implemented B-tree and hash indexes on high-cardinality columns, reducing query execution time by 10-50x on complex joins across 150+ years of player statistics.
  \item Compared views vs materialized views for frequently-accessed data, benchmarking different query formulations.
\end{itemize}

\textbf{Global Air Quality and Health Impact Analysis — Final Project} \hfill ESPM 157, 2024
\begin{itemize}
  \item Investigated relationship between air quality and health outcomes across 175 countries using 5,811+ health records and global AQI datasets; analyzed pollutants (PM2.5, NO2, CO) and their correlation with respiratory and cardiovascular cases.
  \item Discovered South Korea had highest average AQI (421) driven by hazardous PM2.5 levels (415); performed comparative analysis revealing 233-point gap between highest and second-highest countries.
  \item Built interactive Hugging Face application with Python for real-time data exploration; created visualizations using Seaborn, Matplotlib, and pandas to identify high-risk regions and pollutant-health correlations.
\end{itemize}

\textbf{Environmental Justice and Redlining Analysis with Satellite Imagery} \hfill ESPM 157, 2024
\begin{itemize}
  \item Examined systemic racism and environmental justice by analyzing legacy of redlining practices using satellite remote sensing data and spatial analysis techniques.
  \item Worked with spatial vector and raster data at scale; generated high-quality interactive maps displaying environmental disparities across historically redlined neighborhoods.
  \item Computed scientific metrics from remote sensing bands to quantify environmental quality differences; applied geospatial analysis to explore correlations between historical discriminatory housing policies and current environmental conditions.
\end{itemize}

\textbf{Global Fisheries Stock Assessment Analysis} \hfill ESPM 157, 2024
\begin{itemize}
  \item Reproduced and extended analysis from influential Worm et al 2006 paper on global fisheries collapse using modern RAM Legacy Stock Assessment Database accessed via HuggingFace platform.
  \item Mastered relational database concepts by manipulating large-scale tabular data across multiple interconnected tables with different sizes and relationships through various IDs.
  \item Analyzed temporal trends in fish stock health and species collapse patterns; evaluated how fisheries data and conclusions have evolved since original 2006 study using current best-available stock assessment data.
\end{itemize}

\textbf{AI-Powered Tutoring Platform with GPT-3 Integration — Lead Fullstack Developer} \hfill Cubstart, 2024
\begin{itemize}
  \item Directed team of four to develop an AI tutor website utilizing OpenAI GPT-3; focused on backend architecture including API integration with Node.js, secure user authentication, and Firebase data management.
  \item Managed project version control and collaborated with team members to merge features and resolve conflicts effectively.
\end{itemize}

\textbf{Procedural 2D World Generator with Pathfinding} \hfill 2023
\begin{itemize}
  \item Led development of 2D tile-based world generation engine implementing binary space partitioning for random room placement and A* pathfinding algorithm for intelligent NPC navigation.
  \item Designed player interaction system with inventory management and save/load functionality using Java serialization; culminating in 2000+ lines of code and 300 git commits.
\end{itemize}

\textbf{Lethal Company Fast Climbing Mod} \hfill 2023
\begin{itemize}
  \item Modified Unity C\# codebase using Harmony patching to improve player climbing mechanics by 150\%.
  \item Accumulated over 20,000 user downloads and 64 dependencies from other developers on Thunderstore modding platform.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C\#, Java, C++, Go, JavaScript, R, Scheme \\
Web Development & HTML, CSS, React, Node.js, Svelte \\
Database Management & SQL, PostgreSQL, MongoDB, Firebase \\
Data Analysis & NumPy, pandas, scikit-learn, matplotlib, Jupyter Notebook \\
Machine Learning & PyTorch, TensorFlow \\
Computer Graphics & OpenGL, GLSL \\
Game Development & Unity, Unreal Engine 5 \\
Design Tools & Photoshop, VEGAS Pro, After Effects \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% HONORS & AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}
\textbf{CS Scholar} \hfill EECS Department, 2023\\
Selective program supporting first-year students from under-represented backgrounds in Computer Science through cohort-style learning, exclusive seminars, and dedicated advising.

\textbf{Fiat Lux Scholarship} \hfill UC Berkeley, 2022\\
Full-need scholarship for resilient, high-achieving students from partner California high schools, covering full financial need.

\textbf{George C. Marshall Foundation Leadership and Academic Award} \hfill JROTC, 2021\\
National award given to 275 Army ROTC cadets; received as one of 256 JROTC recipients out of 70,000 for reaching JROTC Academic Bowl Championship in Washington D.C.

\textbf{California Boys State Delegate} \hfill American Legion, 2021\\
Appointed Fire Chief of DeVault city; served as elections board judge and senior staff writer for county newspaper.
\end{rSection}

\end{document}
