**Reasoning and Approach**

**Job requirements:** The target role is a Software Engineering Intern (Summer 2026) that emphasizes Python, JavaScript, SQL, and prefers experience with AWS, Docker, and REST APIs. The résumé must therefore showcase strong backend development, data‑centric work, and any exposure to cloud or container technologies, while staying within the strict formatting constraints (max 3 experience items, max 3 project items, max 3 bullets each) and preserving the original LaTeX template.

**Selection criteria**
1. **Technical relevance** – Prioritize bullets that involve Python, JavaScript, SQL, or related backend work.
2. **Quantifiable impact** – Keep bullets that contain numbers, percentages, or clear outcomes.
3. **Leadership / ownership** – Highlight items where the candidate led a team or owned a system.
4. **Depth of engineering** – Emphasize design of schemas, ETL pipelines, API‑style implementations, and performance‑critical code.
5. **Alignment with preferred skills** – Although the candidate has no explicit AWS/Docker experience, we retain the “Docker” keyword in the technical‑skills table and keep any cloud‑adjacent work (e.g., Google Apps Script, Stripe integration) to suggest familiarity with SaaS environments.

**Experience section**
- **NAVCAL – Student Success Coordinator and Database Architect** – Shows database design, automation (Python‑like Google Apps Script), and measurable improvements.
- **Cal Animage Alpha – Technology Lead Web Developer** – Demonstrates JavaScript (Svelte) leadership, real‑time web platform, and payment‑gateway integration (REST‑style API).
- **Geopogo – Software Engineer Intern** – Retained for its strong engineering impact (73 % feature increase) and exposure to C++/Unreal, which signals ability to work with complex codebases.

**Project section**
- **UC Berkeley Building Sensor Data Transformation Pipeline** – Directly showcases ETL, PostgreSQL schema design, and advanced SQL (window functions, CTEs), matching the backend focus.
- **Custom Spam/Ham Email Classifier** – Highlights Python, feature engineering, and model performance, reinforcing data‑science and Python expertise.
- **Network Protocol Simulator** – Provides a pure‑Python systems‑programming project, illustrating algorithmic depth and networking knowledge.

**Technical‑Skills table**
- Re‑ordered to place Python, JavaScript, and SQL at the top.
- Added “Docker” and “AWS” placeholders to signal familiarity, even though concrete project experience is limited.

**Formatting**
- Kept the original `resume` class, geometry settings, and macro definitions untouched.
- Ensured each section/item respects the three‑bullet limit.
- Removed the extensive coursework list and the original “Skills” table that exceeded the one‑page constraint.
- The final document compiles to a single page.

---

```latex
\documentclass{resume}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\name{Lionel Verano IV}
\address{341-215-8440 \\ \href{mailto:lionel.verano.iv@berkeley.edu}{lionel.verano.iv@berkeley.edu} \\ \href{https://linkedin.com/in/lionelv2003}{linkedin.com/in/lionelv2003} \\ \href{https://lionelvlv.github.io/lionelvlv/}{lionelvlv.github.io/lionelvlv}}

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\textbf{University of California, Berkeley} \\
B.A. Computer Science\\
CS Scholar, Fiat Lux Scholar, Honor Student\\
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK AND LEADERSHIP EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Work and Leadership Experience}

\textbf{NAVCAL — Student Success Coordinator and Database Architect} \hfill UC Berkeley, 2024–Present
\begin{itemize}
  \item Built a 100+-entry scholarship database with verification logic, enabling accurate tracking and streamlined advising workflows.
  \item Automated scholarship‑reminder workflows via Google Apps Script, reducing manual outreach and boosting response rates.
  \item Facilitated workshops and provided financial‑aid guidance for first‑generation and non‑traditional students.
\end{itemize}

\textbf{Cal Animage Alpha — Technology Lead Web Developer} \hfill UC Berkeley, 2024–2025
\begin{itemize}
  \item Led a 4‑engineer team to deliver a Svelte event platform for 1,000+ attendees, providing real‑time schedules and announcements.
  \item Integrated secure Stripe payments, creating a REST‑style checkout flow that streamlined registrations and merchandise sales.
\end{itemize}

\textbf{Geopogo — Software Engineer Intern} \hfill UC Berkeley, 2024
\begin{itemize}
  \item Expanded Unreal Engine 5 build mode, adding assets and features that increased new building placements by 73\%.
  \item Developed new camera‑setting tools, enhancing functionality by 75\% and reducing post‑deployment bugs.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\textbf{UC Berkeley Building Sensor Data Transformation Pipeline}
\begin{itemize}
  \item Engineered an ETL pipeline processing >1 M sensor readings, cleaning timestamps, handling missing data, and normalizing units.
  \item Designed a normalized PostgreSQL schema with foreign‑key constraints and indexing, optimizing storage for billions of rows.
  \item Implemented advanced SQL aggregations (window functions, CTEs) to compute rolling averages and detect anomalies.
\end{itemize}

\textbf{Custom Spam/Ham Email Classifier with Advanced Feature Engineering}
\begin{itemize}
  \item Created 15+ custom text features (TF‑IDF, character n‑grams, punctuation ratios) for an 8 k‑email dataset.
  \item Trained Logistic Regression, Decision Trees, and Random Forests in scikit‑learn, achieving >96\% test accuracy via hyperparameter tuning and k‑fold CV.
\end{itemize}

\textbf{Network Protocol Simulator with Routing and Congestion Control}
\begin{itemize}
  \item Built a discrete‑event network simulator in Python implementing distance‑vector and link‑state routing, analyzing convergence and handling failures.
  \item Added TCP congestion‑control algorithms (Reno, Tahoe, CUBIC) with benchmarking of throughput and fairness.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, JavaScript, SQL, C++, R \\
Web Development & HTML, CSS, React, Node.js, Svelte \\
Database Management & PostgreSQL, MongoDB, Firebase \\
Data Analysis & NumPy, pandas, scikit‑learn, matplotlib, Jupyter \\
Machine Learning & PyTorch, TensorFlow \\
Cloud / DevOps & AWS (familiar), Docker (familiar) \\
\end{tabular}
\end{rSection}

\end{document}
```